\bf\large \MakeUppercase{\papertitle{}}

### 2020-11-23 2020/GVSETS_2020/GVSETS.tex

@@

%% ============================================================
\bibliographystyle{unsrt}
\bibliography{Bib/refsAutonomousVehicles,Bib/refsMachineLearning,Bib/refsChronoSpecific,Bib/refsCompSci,Bib/refsDEM,Bib/refsFSI,Bib/refsGraphics,Bib/refsMBS,Bib/refsRobotics,Bib/refsSBELspecific,Bib/refsSensors,Bib/refsTerramech,Bib/refsDRL}

>>>>

\usepackage{biblatex}
\addbibresource{../../bibliography/refsAutonomousVehicles.bib,Bib/refsMachineLearning,../../bibliography/refsChronoSpecific.bib,../../bibliography/refsCompSci,../../bibliography/refsDEM.bib,../../bibliography/refsFSI.bib,Bib/refsGraphics.bib,../../bibliography/refsMBS.bib,../../bibliography/refsRobotics.bib,../../bibliography/refsSBELspecific.bib,../../bibliography/refsSensors.bib,../../bibliography/refsTerramech.bib,../../bibliography/refDRL.bib}
\addbibresource{../../bibliography/refDRL.bib}
\addbibresource{../../bibliography/refsMBS.bib}

@@

%% ============================================================
\printbibliography
